\cvsection{Experience}

\begin{cventries}
	
  \cventry
	{Projects}
	{Astrophysics Researcher \vspace{1mm}}
	{UC Santa Cruz}
	{2016-2019}
	{
		\vspace{0.1cm}
		\begin{cvitems}
			\item {\textbf{Stellar Mass Binary Black Hole Systems}
				\begin{itemize}
					\item Studied stellar mass binary black hole systems resulting in two refereed-journal publications, including one first-author paper.
					\item Used Python to create initial condition files for the hydrodynamic code, GADGET, to run simulations of these systems. 
					\item Used Python to create visualizations and perform statistical analysis for the publication.
					\item Used visualization software to create animations of simulation output.
				\end{itemize}}			
			\item {\textbf{Eccentric X-ray Binary Systems}
				\begin{itemize}
					\item Successfully implemented binary stellar wind emission into the hydrodynamic simulation code written in Fortran, FLASH. 
					\item Used Python to visualize and analyze simulation output to study mass accretion rates, eccentricity time dependecy, and fluid stream morphology.
				\end{itemize}} 
			\item {\textbf{Red Giant - Star Collisions:} 
				\begin{itemize}
				\item Presented a poster our findings to a multi-disciplinary audience.
				\item Used the Python package NumPy to simulate collisions using meshgrids.
				\item Used Python to cteate initial conditions for simulations run in the hydrodynamic code, GADGET.
				\item Used visualization software to create animated visualizations of GADGET simulations.
				\item Used Python to create visualizations for poster. 
				\end{itemize}}
		\end{cvitems}
	}
	  
  
\end{cventries}
